\chapter{Social Intranet: Document Management}

Enterprise social networks (Chatter, Yammer, Socialcast, Jive). Microsoft has
SkyeDrive, but the social component in SharePoint is very weak. Thus, Microsoft
later bought Yammer (Sect.\ref{sec:Yammer}).

Perhaps the two most famous brands in the history of enterprise software, Lotus
and SharePoint, will soon disappear. We mean brands, not specific products.
Because by renaming their products, vendors try to erase the association with
outdated technologies in customer brain. 

\section{OpenKM (open-source)}
\label{sec:OpenKM}

OpenKM is a web base document management application that uses standards and Open Source technologies.

OpenKM provides full document management capabilities including version control
and file history, metadata, scanning, workflow, search, and more.
The social activities around the content connect people to other people,
information to information, and people to information; helping to manage, more
efficiently, the collective intelligence of the human resources of the company.

While not quite as polished as some of the other open-source document management
systems, OpenKM also offers enterprise-ready capabilities. Key features include
drag-and-drop functionality, a powerful search engine, and tag clouds. Operating
System: OS Independent.

OpenKM Replaces: Documentum, Microsoft SharePoint, OpenText


OpenKM provides free features (Community version), and commercial features (Professional version):
\url{http://wiki.openkm.com/index.php/User_Guide}

\section{Nuxeo (open-source)}
\label{sec:Nuxeo}

Alfresco vs Nuxeo vs OpenKM:
\url{http://www.slideshare.net/nuxeo/comparing-the-code-quality-of-ecms}

\section{Epiware (open-source)}
\label{sec:EpiWare}



\section{Yammer (social intranet)}
\label{sec:Yammer}

Yammer is revolutionizing internal corporate communications by bringing together
all of a company's employees inside a private and secure enterprise social
network.

Using Yammer is like using Facebook or Twitter, but it is an enterprise-class
software built from the ground up to drive business objectives.

Yammer was bought by Microsoft in 2012.
Microsoft bought Yammer not for the engine, but for the customer base and the
image of  social vendor.
In June 2013, Office 365 users got the opportunity to replace SharePoint
Newsfeed to Yammer, and Microsoft continues to insist that Yammer - is its
future and that soon Yammer will become the platform for all its business apps.
Yammer - is purely SaaS service (Sect.\ref{sec:SaaS}), and for the companies
that use local SharePoint server and aren't ready to move to SaaS, Newsfeed
remains the primary solution.


\section{SharePoint + SkyeDrive}
\label{sec:SharePoint}

Organizations use SharePoint to create websites. You can use it as a secure
place to store, organize, share, and access information from almost any device.
All you need is a web browser, such as Internet Explorer, Chrome, or Firefox.


SharePoint is not a front-end, but a back-end instead, which provides
\begin{itemize}
  \item framework for web app development
  
  \item multi-purpose platform allows for managing and provisioning of intranet portals, extranets and websites, document management and file management,
  
  \item collaboration spaces, social networking tools, enterprise search, business intelligence tooling
  
  \item process/information integration, and third-party developed solutions
\end{itemize}

SharePoint is a toolsuite with many products
\begin{enumerate}
  \item SharePoint Online
  \item SharePoint Foundation
  \item SharePoint Server
  \item sharePoint Designer 2013
  \item OneDrive for Business folder sync: Desktop-app
\end{enumerate}
\url{https://support.office.com/en-za/article/What-is-SharePoint-97b915e6-651b-43b2-827d-fb25777f446f}

\url{http://blog.apterainc.com/bid/316563/What-is-Microsoft-SharePoint-Used-For}

\url{http://www.liventerprise.com/compare/OpenKM_vs_SharePoint/}

\section{IBM Lotus Notes}

Lotus appeared back in the 80-s years of last century. In 1995 IBM acquired
Lotus Development and began selling their products Lotus Notes/Domino. In the
following years most IBM collaboration systems moved under the Lotus umbrella.
But last year the revolution occurred. The last child of the Lotus family - SaaS
suite LotusLive was renamed to SmartCloud for Social Business. And then the name
Lotus was removed from other products. The final nail was the recent launch of
Notes/Domino 9.0 Social Edition (without Lotus).


\section{Dropbox for Enterprise}


\section{Chatter (Saleforce)}
\label{sec:Chatter}

With Chatter, it's easy to work together and know everything that's happening in your company.

\url{http://www.liventerprise.com/tool/Salesforce_Chatter/}


\section{Google Apps (web-based, internet-capable)}

Google Apps offer completely browser-based office applications like a word
processor and spreadsheet, as well as communication tools like chat and email,
as well as collaboration tools like project managers and wikis.

\section{Zoho's Office suites (web-based)}

Zoho offer completely browser-based office applications like a word processor
and spreadsheet, as well as communication tools like chat and email, as well as
collaboration tools like project managers and wikis.

\url{http://lifehacker.com/315256/zoho-suite-vs-google-docs}

